% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Scholarships and additional info
\sectionTitle{Publications}{\faBook}

\begin{scholarship}
  \scholarshipentry{2022}
  {
    Numerical investigation of continuous-flow ternary separation of particles
    in a microchannel with a wall-mounted obstacle using Dielectrophoresis
    (\emph{Under review by the \href{supervisor}{supervisor}})
 \vspace{10pt}
  \begin{itemize}

    \item The idea is to place a trapezoidal obstacle in the channel to create
        a gradient in momentum (in the lateral direction) so that in regions
        closer to the obstacle, mid-size particles experience greater drag force
        and pass over the planar-angled electrode pair.\vspace{10pt}

    \item We assumed that the fluid flow influences the motion of the particles, but
          the particles have a negligible effect on the fluid flow (one-way
          coupling).\vspace{10pt}

    \item We extend the OpenFOAM solvers,
          \texttt{icoUncoupledKinematicParcelFoam} and \texttt{simpleFoam}, to
          solve for discrete and continuous phase, respectively. Further,
          the Dielectrophoretic force on particles has been implemented, by
          deriving from the abstract base class template \texttt{ParticleForces}
          (especifically, the \texttt{calcNonCoupled} member function).
  \vspace{10pt}
    \item The code code is validated by performing experimental tests using
      a microdevice previously fabricated in our lab.

  \end{itemize}
}

\scholarshipentry{2020}
{
  Outokesh, Masoud, Seyed Soheil Mousavi Ajarostaghi, \emph{Ali Bozorgzadeh}, and Kurosh Sedighi. "Numerical evaluation of the effect of utilizing twisted tape with curved profile as a turbulator on heat transfer enhancement in a pipe." Journal of Thermal Analysis and Calorimetry 140, no. 3 (2020): 1537-1553. (\href{https://link.springer.com/article/10.1007/s10973-020-09336-0}{link})
  }

\end{scholarship}
